DDSAnalytics  - Employee Trends

### 2018-04-16 msds6371-group-project-kaggle.Rmd

## Question 2

@@

@@

##### Assumptions
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

@@

##### Assumptions
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

@@

##### Assumptions
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

### Comparison of Models
| Predictive Models | Adusted R^2 | CV Press | Kaggle Score |
|-------------------|:-----------:|:--------:|:------------:|
| Forward           | 0.1111      | 1111     | .111         |
| Backward          | 0.2222      | 2222     | .222         |
| Stepwise          | 0.3333      | 3333     | .333         |
| Custom            | 0.4444      | 4444     | .444         |

>>>>

\pagebreak
## Question 2

@@

Build the most predictive model for sales prices of homes in all of Ames Iowa.  By using  4 models: one from forward selection, one from backwards elimination, one from stepwise selection, and one the build custom.

The custom model is one of the three preceding models .  The  custom model  is the best in terms of being able to predict future sale prices of homes .

@@

##### Assumptions

The Forward selection model is satisfying all below condition after performing transfermation on some of the variables.
* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

After accounting for all other possible confounders (that we measured), and holding them fixed, we estimate that for each additional $100 spent on a student in the U.S. (excluding Alaska), his or her estimated SAT score increases 3.38514 points (p-value from MLR < .0001).  A 95% confidence interval is (1.82, 4.95) points.

@@

##### Assumptions

* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

@@

##### Assumptions

* Linear Trend (Plots: Response vs Explanatory, Explanatory vs Explanatory)
* Normality (Residual: Scatter, QQ Plot, Histogram)
* Equal Standard Deviation (Residual Scatter Plots)

### Comparison of Models

| Predictive Models | Adusted R^2 | CV Press | Kaggle Score |
|-------------------|:-----------:|:--------:|:------------:|
| Forward           | 0.8801      | 23.6     | .201         |
| Backward          | 0.8801      | 23.3     | .201         |
| Stepwise          | 0.8801      | 23.8     | .201         |
| Custom*           | 0.8518      | 23.2     | .201         |

 * custom method choosen was Forward(select=SL)
### Conclusion

Based on after accounting for all other possible confounders (that we measured), and holding them fixed, we estimate that for each additional $100 spent on a student in the U.S. (excluding Alaska), his or her estimated SAT score increases 3.38514 points (p-value from MLR < .0001).  A 95% confidence interval is (1.82, 4.95) points.
